Cell-type diversity and connectome of the ctenophore apical organ

### 2024-04-11 manuscript/Manuscript.qmd
add commenting functionality to html output with hypothes.is
Fig: celltype network

---
title: "Cell-type diversity and connectome of the ctenophore apical organ"
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
max-width: 100%
format:
  html: default
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

@@

knitr::include_graphics("figures/Figure2.png")
```

@@

>>>>

---
title: "Cell-type diversity and connectome of the ctenophore apical organ"
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
max-width: 100%
format:
  html:
    embed-resources: true 
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

@@

knitr::include_graphics("figures/Figure_network.png")
```

@@

<!--
## See https://github.com/hypothesis/client
## Add commenting functionality with this script
-->

<script src="hypothes.is/embed.js" async></script>
